---
title: "Processing ONT Duplex Samples"
author: "Jake Reed"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Processing ONT Duplex Samples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  collapse = TRUE,
  comment = "#>"
)
```

# 1. Installation
This package depends on MEME and minimap2. MEME is a motif analysis tool which is used to determine the most common telomere motifs in a reference genome. Minimap2 is a read aligner which is used to align reads to the reference genome. Both of these tools are required for the package to run.

## Install MEME
Download the software from https://meme-suite.org/meme/doc/download.html
Type the following commands: 

```{bash, eval = FALSE}
tar -zxf meme-5.5.7.tar.gz
cd meme-5.5.7
./configure --prefix=$HOME/meme --enable-build-libxml2 --enable-build-libxslt
make
make test
make install

# Edit your shell configuration file to add $HOME/meme/bin and $HOME/meme/libexec/meme-5.5.7 to your shell's path. This can often be done by editing the file named .profile to add the following line:

export PATH=$HOME/meme/bin:$HOME/meme/libexec/meme-5.5.7:$PATH
```

## Install minimap2
```{bash, eval = FALSE}
git clone https://github.com/lh3/minimap2
cd minimap2 && make
```


## Data
The data for running this full vignette can be downloaded from the SRA database using the following commands:
A section of this vignette from [fill in later] to the end can be run using [fill in later] data from within the package.
```{bash, eval = FALSE}
# Download SRA toolkit
wget --output-document sratoolkit.tar.gz https://ftp-trace.ncbi.nlm.nih.gov/sra/sdk/current/sratoolkit.current-ubuntu64.tar.gz
tar -vxzf sratoolkit.tar.gz
export PATH=$PATH:$PWD/sratoolkit.3.0.0-mac64/bin

# Download fastq file
prefetch --progress --resume yes -X 500G SRR28295757
fastq-dump SRR28295757
```

# 2. Showcase
## Load Libraries and Samples
```{r libraries}
# Load libraries
library(TECAT)
library(ggplot2)
library(cowplot)

# Sample name
sample_name <- "HG002"

# Load the TECAT package data
extdata <- system.file("extdata", package = "TECAT")
if(extdata == "") {
  # Fallback for when package isn't installed (during development/build)
  if(file.exists("~/cran/tecat/inst/extdata")) {
    extdata <- "~/cran/tecat/inst/extdata"
  } else {
    stop("Cannot find package extdata directory")
  }
}

#sample_file <- file.path("/path/to/sra_fastq/")
reference_file <- file.path(extdata, "chr_ends.fa.gz")
data_dir <- tempdir()
results_dir <- file.path("~/tmp", sample_name, "results")
dir.create(results_dir, showWarnings = FALSE, recursive = TRUE)

# Set options
options(width = 300)
options(meme_bin = "~/meme/bin")

# Set number of threads
threads <- 2
```

## Process Fastq
This process is used in order to split files in order to support efficient parallelization. 
Ideally, you would set `target_ram_size_gb` * `threads` to be equal to something near the 
total RAM for your machine. The fastq file can be downloaded from the SRA database using
SRA toolkit. Here are the commands you would use to download the fastq file for this
experiment. 

```{r Split_Fastq, eval = FALSE}
# Split large fastq file into files that will occupy
# 2GB of RAM in order to take advantage of all processors
# (20) with given RAM (62GB).
if (!file.exists(list.files(file.path(dirname(sample_file), "split"),
  full.names = TRUE
)[1])) {
  stats_fl <- auto_split(
    in_fastq = sample_file,
    prefix = sample_name,
    threads = threads,
    out_dir = file.path(data_dir, "split"),
    target_ram_size_gb = 2
  )

  # Save stats
  saveRDS(stats_fl, file.path(
    results_dir,
    "stats_fl.rds"
  ))
}
```

## Process Reference Fastq
```{r denovo motif finding, eval = FALSE}
# ONT Settings
motif_analysis <- telomere_motif(
  reference_file = reference_file,
  reference_telo_length = 2000,
  telo_motif_length = 6,
  number_of_motifs = 10,
  number_of_repeats = 10,
  platform = "ONT",
  threads = threads
)

print(paste("Number of motifs found: ", length(motif_analysis$motifs)))
cat("\n")
print(paste(
  "Grep pattern for pattern matching and initial search: ",
  motif_analysis$grep_list
))

# Save results
saveRDS(motif_analysis, file.path(results_dir, "motif_analysis_results.rds"))

# Clean up
gc()
```

## Isolate telomere reads
```{r telo_search, eval = FALSE}
# Run pattern searh on all split fastq files
file_list <- list.files(file.path(data_dir, "split"),
  full.names = TRUE
)

# Create output directory
out <- file.path(data_dir, "telo")
dir.create(out, showWarnings = FALSE)

# Search telomeres
## Need to explain in documentation that threads should match number of files
## This function requires > 4 GB of memory per thread. 
search_res <- telo_search(
  fastq_files = file_list,
  grep_list = motif_analysis$grep_list,
  threads = threads,
  out_dir = out,
  return_telomeres = FALSE,
  verbose = FALSE,
  progress = TRUE
)

# Print some basic telomere finding statistics
head(search_res$telomere_stats)

# Save telomere_stats
saveRDS(search_res, file.path(
  results_dir,
  "telomere_stats.rds"
))

# Clean up
rm(list = c("file_list", "out"))
gc()
```

## Cut telomere reads into sliding windows
## If you are running this vignette without the full data set, start here and run this opts_chunk
```{r load telomere file, eval = TRUE}
telomere_stats <- readRDS(file.path(
  extdata,
  "telomere_stats.rds"
))

telo_file <- file.path(extdata, "combined_telo.fa.gz")
```

```{r telo_cut, eval = TRUE}
# Run sliding window on all telomere files
windows <- sliding_window_parallel(
  telomere_file = telo_file,
  window_length = 200,
  step = 100,
  environment = "linux",
  threads = threads
)

# Save windows
saveRDS(windows, file.path(
  results_dir,
  "windows.rds"
))
# Satus
cat("\nFinished processing all telomere files to sliding windows.", "\n")
```

## Calculate frequency of telomere motifs in sliding windows
```{r telo_freq, eval = TRUE}
# Load in data
motif_analysis <- readRDS(file.path(
  extdata,
  "motif_analysis_results.rds"
))
motifs <- as.character(motif_analysis$motifs)

# Directories
win_file <- file.path(
  results_dir,
  "windows.rds"
)

# For loop over all telomere windows files
wins <- readRDS(win_file)
length(wins)

dir.create(file.path(results_dir, "frequencies"),
  showWarnings = FALSE
)

out_dir <- file.path(
  results_dir,
  "frequencies"
)
# Test
freqs <- frequencies(
  windows = wins,
  motifs = motifs,
  environment = "linux",
  parallel = TRUE,
  threads = threads,
  save_files = TRUE,
  progress = TRUE,
  out_dir = out_dir,
  verbose = FALSE
)

# Save Frequencies
saveRDS(freqs, file.path(
  results_dir,
  "freqs.rds"
))
cat("\nNumber of telomeres found: ", length(freqs), "\n")
cat("\nExample telomere frequencies:\n")
knitr::kable(head(freqs[[1]]))
cat("\n...")
knitr::kable(tail(freqs[[1]]))

# Clean up
rm(list = setdiff(ls(), c(
  "freqs",
  "paths",
  "sample_name",
  "results_dir", 
  "extdata", 
  "reference_file", 
  "data_dir", 
  "threads"
)))
gc()
```

# Determine telomere length
This data frame is produced from a subset of the data, and the following runs the method on all start and end threshold combinations. This allows 
for the next step to determine the optimal thresholds to use for the rest of the data.
```{r telomere_length, eval = TRUE}
# Load data
telomere_frequencies <- readRDS(file.path(
  results_dir,
  "freqs.rds"
))

# Threshold determination
thresh_df <- determine_threshold(
  telomere_list = telomere_frequencies,
  threads = threads,
  sample_ratio = 0.025
)

# Save threshold data
saveRDS(thresh_df, file.path(
  results_dir,
  "threshold_data.rds"
))
```

## Reformat Threshold Data
This section reformats the threshold data in order to facilitate visualization of the data in the next step.
```{r formatting, eval =  TRUE}
# Start sensitivity
start_number_of_telos <- unlist(lapply(thresh_df$start, function(x) {
  length(which(!is.na(x$telomere_end)))
}))
sensitivity_df <- data.frame(
  start = seq(1, 100, 1),
  end = rep(5, 100),
  number_of_telos = start_number_of_telos
)

# Telomere length
# End telomere length
telomere_lengths_end <- lapply(thresh_df$end, function(x) {
  vals <- x$telomere_length[!is.na(x$telomere_end)]
  x <- mean(vals)
  if (x != 0 & length(vals) > 1) {
    std_dev <- stats::sd(vals)
  } else {
    std_dev <- 0
  }
  ret_frame <- data.frame(
    mean = x,
    std_dev = std_dev
  )
  return(ret_frame)
})
end_df <- do.call(rbind, telomere_lengths_end)
telomere_length_df <- cbind(
  start = rep(20, 100),
  end = seq(1, 100, 1),
  end_df
)

# Print data
print(paste0("\nStart sensitivity data:"))
knitr::kable(head(sensitivity_df))
print(paste0("\n..."))
knitr::kable(tail(sensitivity_df))
print(paste0("\n"))

print(paste0("\nTelomere length data:"))
knitr::kable(head(telomere_length_df))
print(paste0("\n..."))
knitr::kable(tail(telomere_length_df))
```

# Find optimal thresholds
The method determines telomere boundaries using two threshold values for telomere frequency motifs in 200 bp rolling windows. 
The start threshold sets the minimum motif frequency required in the first window to identify a telomeric region, affecting the 
method's sensitivity. The end threshold defines the minimum motif frequency that determines where the telomeric region ends - when 
a window falls below this threshold, that position marks the telomere length for that read. An optimal start threshold balances sensitivity, 
while the end threshold ensures accurate telomere length determination. The method's performance hinges on these thresholds, as they directly
influence the identification and measurement of telomeric regions in the sequencing data.
```{r find_optimal_thresholds, eval = TRUE}
thresholds <- optimal_thresholds(threshold_dataframe = thresh_df)
thresholds
```

## Visualize Threshold data
We visualize how different start and stop threshold combinations affect both the number of identified telomeres and their average length to 
evaluate the telomere length determination method.
```{r plot_threshold_data, eval = TRUE}
# Plot sensitivity and telomere line graphs next to each other
sens_plot <- ggplot(sensitivity_df, aes(x = start, y = number_of_telos)) +
  geom_line() +
  geom_point() +
  geom_vline(xintercept = thresholds$sensitivity, color = "red") +
  labs(
    x = "Start Threshold",
    y = "Number of Telomeres",
    title = "Telomere Sensitivity"
  ) +
  theme_bw()

telomere_plot <- ggplot(telomere_length_df, aes(x = end, y = mean)) +
  geom_line() +
  geom_point() +
  geom_vline(xintercept = thresholds$telomere, color = "red") +
  labs(
    x = "End Threshold",
    y = "Telomere Length",
    title = "Telomere Length"
  ) +
  theme_bw()

plot_grid(sens_plot, telomere_plot, ncol = 2)

# Print best thresholds
best_start <- sensitivity_df$start[which.max(sensitivity_df$number_of_telos)]
print(paste0("\nBest start threshold: ", best_start, "\n"))
best_end <- telomere_length_df$end[which.max(telomere_length_df$mean)]
print(paste0("\nBest end threshold: ", best_end, "\n"))
```

## Determine optimal thresholds
We use the optimal thresholds found in the previous step and apply them to the entire dataset in order to determine telomere lengths.
```{r check_lengths, eval = TRUE}
# Load data
telomere_frequencies <- readRDS(file.path(
  results_dir,
  "freqs.rds"
))

# Setup parallel environment
cl <- parallel::makeCluster(threads)
parallel::clusterExport(cl, c("findTelLength"),
  envir = environment()
)

# Load plyr inside the cluster only
invisible(parallel::clusterEvalQ(cl, {
  if (!requireNamespace("plyr", quietly = TRUE)) {
    stop("plyr package is needed for this vignette")
  }
  library(plyr)
  NULL
}))

results <- invisible(parallel::parLapply(cl, telomere_frequencies,
  findTelLength,
  st.thresh = thresholds$sensitivity,
  en.thresh = thresholds$telomere_length
))

# Stop the cluster
parallel::stopCluster(cl)

results_df <- do.call(rbind.data.frame, results)

head(results_df)

# Save results
saveRDS(results_df, file.path(
  results_dir,
  "results_df.rds"
))

# Look at average length in telomeres
telomere_lengths <- results_df$telomere_length[which(!is.na(results_df$telomere_end) &
  results_df$telomere_length > 0)]

# Print fraction na
print(paste0("Fraction NA: ", sum(is.na(results_df$telomere_end)) / nrow(results_df)))

# Telomere update print(paste0)
print(paste0("Number of telomeres found: ", length(telomere_lengths), "\n"))
wo_na <- results_df[!is.na(results_df$telomere_end), ]
print(paste0("Mean telomere length at 20-15 without NA: ", mean(wo_na$telomere_length)))

# Add this check before creating the histogram
if(length(telomere_lengths) > 1) {
  # Calculate number of breaks, ensuring a minimum of 2
  num_breaks <- max(2, round(sqrt(length(telomere_lengths))))
  
  # Create histogram of telomere lengths
  hist(telomere_lengths,
    breaks = num_breaks,
    main = "Histogram of Telomere Lengths",
    xlab = "Telomere Length (bp)",
    ylab = "Frequency"
  )
} else {
  # Create an empty plot with a message when insufficient data
  plot(0, 0, type = "n", axes = FALSE, xlab = "", ylab = "")
  text(0, 0, "Insufficient telomere length data for histogram", cex = 1.5)
}
```

# Truncation and Mapping
After identifying the telomeric region, the method trims the read at this boundary and maps the remaining sequence to the reference genome.
```{r truncate, eval = TRUE}
# Load data
results_df <- readRDS(file.path(
  results_dir,
  "results_df.rds"
))

# Remove NAs
results_df <- results_df[!is.na(results_df$telomere_end), ]
ls()
find_sizes()

telomere_file <- file.path(extdata, "combined_telo.fa.gz")
#telomere_file <- file.path(data_dir, "telo", "combined_telo.fa.gz")
ref_file <- reference_file

# Truncate telomeres
trunc_dir <- file.path(data_dir, "trunc")
dir.create(trunc_dir, showWarnings = FALSE)

# Truncate files
fasta_fl <- truncate_file(
  combined_telomere_file = telomere_file,
  results_data_frame = results_df,
  out_dir = trunc_dir,
  write_file = TRUE,
  return = FALSE
)

# Map reads to reference
combined_fasta <- file.path(trunc_dir, "truncated_reads.fa")
map_dir <- file.path(data_dir, "map")
dir.create(map_dir, showWarnings = FALSE)

# Map reads
mapped_output <- map(
  fasta = combined_fasta,
  results_data_frame = results_df,
  reference_file = ref_file,
  preset_string = "map-ont",
  out_dir = map_dir,
  return_mapped = TRUE,
  threads = threads
)

# Check if mapping was successful
mapped_output$results

# Save mapped output
saveRDS(mapped_output, file.path(
  results_dir,
  "mapped_output.rds"
))
```

# Plotting
```{r violin_plot, eval = TRUE, fig.width = 12, fig.height = 8}
# Load data
mapped_output <- readRDS(file.path(
  results_dir,
  "mapped_output.rds"
))

mapped_output$results

# Add a check before trying to modify the data frame
if (nrow(mapped_output$results) > 0) {
  mapped_output$results$sample <- sample_name
  
  # Create violin plot of mapped_output with top and bottom panels
  library(extrafont)
  loadfonts()
  
  chromesome_plt <- tecat_plot(mapped_output = mapped_output,
    out_dir = results_dir,
    prefix = sample_name, 
    save_plots = TRUE,
    return = TRUE)
  
  # Print the chromesome plot
  chromesome_plt
} else {
  # Create a placeholder message or simple plot when data is missing
  plot(0, 0, type = "n", axes = FALSE, xlab = "", ylab = "")
  text(0, 0, "No mapping results available for plotting", cex = 1.5)
}
```

# Exporting Results
Produce CSV table of results.
```{r empty}
data <- mapped_output$results

if (!is.null(data) && nrow(data) > 0) {
  head(data)
  new <- data.frame(data[, c(1:13)])
  rand_telo <- round(rnorm(nrow(new),
    mean = mean(data$telomere_length, na.rm = TRUE),
    sd = stats::sd(data$telomere_length, na.rm = TRUE)
  ))

  # Save csv file
  write.csv(data, file = file.path(
    results_dir,
    "output_results.csv"
  ))
} else {
  message("No data available to export.")
}
```

# Run RShiny
```{r shiny, eval = FALSE}
# Run RShiny
launch_dashboard()
```

# Session Info
```{r session_info}
sessionInfo()
```

